pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-02-28 article.tex
Example 2 worked out better

Figure \ref{fig:example_2} shows that the best candidate model gives an error distribution 
with an HPD at 0.02. The range of errors goes from 0.0 to 0.08. 
\richel{Describe and show evidences for the candidate model}
\richel{Describe and show the best candidate model}
This means that it is rational to use this inference model to 
infer a posterior phylogeny distribution, 
as is done by \verb;pirouette;.
\richel{Show effective sample size}
\richel{Show posterior phylogenies as densitree}

@@

>>>>

Figure \ref{fig:example_2} shows that the best candidate model gives an error distribution 
with an HPD at 0.02. The range of errors goes from 0.0 to 0.08. 
The inference model with the highest evidence follows a JC site model, 
RLN clock model and BD tree prior, with a weight of $0.675$. 
This is (unexpectedly) better than the generative
model with a weight of $0.166$. 
The complete list of all evidences is shown in table \ref{tab:evidences_example_2}.
This means that it is rational to use this inference model to 
infer a posterior phylogeny distribution, 
as is done by \verb;pirouette;.
Also here, the ESSes are well above 200, 
as shown in table \ref{tab:esses_example_2}.

@@

\input{example_2_esses.latex}
% has label tab:esses_example_2

\input{example_2_evidences.latex}
% has label tab:evidences_example_2
